\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-09-28 sections/results.tex
Add: Analysis for Figure 7 (text)

  % TODO: Statistical test for differences + Refer to original paper and create conclusions

  Prevotella and Clostridiales are shown to have consistent evidence of association with ASD diagnostic status [REFS - Ho et al., 2020].
  Notably, the abundance of these genera are lowered in cases with

  We observed 20 unique links in the network for control samples, 12 unique links in the network for ASD subjects and 7 edges in common between both networks.
  These unique connections can serve as potential starting points for literature surveys and further experimental confirmations.

>>>>

  The analysis of the rewiring of associations in the ASD samples with respect to the control provides a guide for identification of key genera that could be linked to dysbiosis.
  We observed 20 unique links in the network for control samples, 12 unique links in the network for ASD subjects and 7 edges in common between both networks.
  Although these unique connections do not imply real interactions, they can still serve as potential starting points for literature surveys and further experimental confirmations.
  For example, the changed connectivity of Prevotella and Porphyromonas in our networks show that these genera could be useful candidates for further downstream verification.
  Correspondingly, we have found previous studies that indicate that these genera are implicated in ASD~\cite{Kang2017,hoGutMicrobiotaChanges2020} and cognitive impairment~\cite{chiPorphyromonasGingivalisInducedCognitive2021}.
